A robust DPG method for convection-dominated diffusion problems II: adjoint boundary conditions and mesh-dependent test norms.

### 2013-05-01 docs/Jesse/HeuerPaper/responseForReviewers2.tex

\signature{Jesse Chan, Norbert Heuer, Tan Bui-Thanh, and Leszek Demkowicz}
\address{201 East 24th St, Stop C0200\\
Austin, Texas 78712-1229}
\begin{document}
\begin{letter}{Dr Alexey Chernov\\CAMWA Guest Editor\\Special Issue: HONAPDE 2012}

%\tableofcontents
%\maketitle

\opening{Dear Dr Chernov,}

The authors are very grateful for the feedback, comments and suggestions provided by both reviewers in this revision.  Please accept the attached second revised version of our paper.

@@

\textbf{Reviewer 2}

\begin{enumerate}
\item \textcolor{red}{p. 4, footnote: given that the authors are in a Hilbert space setting, the authors probably mean $\nor{v}_{V(\Oh)}^2 = \sum_{K\in \Oh} \nor{v}_{V(K)}^2$.}  Corrected -- the authors thank the reviewer for noting this.
\item \textcolor{red}{Section 1.3: the claim about the relation between the norms $\nor{\cdot}_U$ and $\nor{\cdot}_{V,U}$ is not completely clear to the referee--the authors are encouraged to add a few clarifying words:}
\begin{enumerate}
\item \textcolor{red}{please give a precise reference to a theorem in [5].} Clarified.  The theorem is specified to be Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}.  
\item \textcolor{red}{please be more specific as to what ``definite" means for the bilinear form.} Clarified.  We have added a footnote clarifying the ``definiteness" of the bilinear form as meaning 
\[
b(u,v) = 0, \forall v\in V \Rightarrow u = 0
\]
and
\[
b(u,v)=0, \forall u\in U \Rightarrow v = 0,
\]
 which imply injectivity of the bilinear operator $B$ and its transpose $B'$, defined such that $\LRa{Bu,v} = \LRa{u,B'v}.$  These conditions in turn guarantee (through the Banach closed range theorem) solvability of the variational problem.
\item \textcolor{red}{the discussion in Section $1.3$ suggests that for any norm $\nor{\cdot}_U$ one has an induced norm $\nor{\cdot}_{V,U}$ on $V$ . The referee doesn't see this. For example, taking $U = V = H_0^1(\Omega)$ and $b(u, v) \coloneqq \LRp{\grad u,\grad v}_{L^2(\Omega)}$ but equipping $U$ with $\nor{\cdot}_U \coloneqq \nor{\cdot}_{L^2(\Omega)}$ does not lead to a norm on $V$ via $\nor{\cdot}_{V,U}$ , since for smooth $v$ one obtains $\nor{v}_{V,U} = \nor{\del v}_{L^2(\Omega)}$.}  
\begin{enumerate}
\item At a very broad level, from Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a}, the duality between trial and test norms is a consequence of $M/\gamma = 1$, where $M$ is the continuity constant such that $b(u,v)\leq M \nor{u}_U\nor{v}_V$, and $\gamma$ is the inf-sup/boundedness below constant such that 
\[
0<\gamma \leq \inf_{u\in U}\sup_{v\in V}\frac{b(u,v)}{\nor{u}_U\nor{v}_V}.
\]
If the problem is posed such that $U = H_0^1$ but $\nor{\cdot}_U = \nor{\cdot}_{\L}$, then this problem is ill-posed and we no longer have duality between trial and test norms.

\item The reason for the loss of well-posedness if we choose $U = H_0^1$ and $\nor{\cdot}_U = \nor{\cdot}_{\L}$ is that the space $U = H_0^1$ is not complete under the norm $\nor{\cdot}_U = \nor{\cdot}_{\L}$.  In other words, the space $U$ is smaller than the $\L$ norm would imply - a weaker norm $\nor{\cdot}_U$ implies a large space $U$.  Under the perspective that the spaces $U$ and $V$ are defined by their respective norms, if we set $\nor{\cdot}_U = \nor{\cdot}_{\L}$, this would imply $U = \L$. Since the definitions of the spaces $U$ and $V$ are incorporated in the definition of definiteness of $b(u,v)$, we would lose definiteness of the bilinear form as well, a prerequisite for Lemma 2.5.  
\item We note that it is still possible to specify $\nor{\cdot}_U = \nor{\cdot}_{\L}$.  If we do not require $U = V = H_0^1$, and simply specify $\nor{\cdot}_U = \nor{\cdot}_{\L}$, then the space induced by $\nor{\cdot}_U$ is $U = \L$.  If, then, we rewrite the bilinear form such that $b(u,v) = -\LRp{u,\del v}_{\L}$ (to satisfy regularity constraints), then we do indeed induce the norm $\nor{v}_V \coloneqq \nor{\del v}_{\L}$, which then induces the definition of the test space $V = \LRc{v\in \L, \del v\in \L}$.  Under these conditions, we can show that both well-posedness and duality of norms hold.

\end{enumerate}
There are two main responses to this question - the first is that the definition of a space cannot be divorced from the definition of the norm on the space (by choosing a norm on $U$, we are simultaneously choosing the space $U$).  The second Lemma 2.5 in \cite{Bui-ThanhDemkowiczGhattas11a} gives that three conditions are equivalent - 
\begin{itemize}
\item $\frac{M}{\gamma} = 1$
\item $\nor{\cdot}_U = \sup_{v\in V}\frac{b(u,v)}{\nor{v}_V}$
\item $\nor{\cdot}_{V,U} = \sup_{u\in U}\frac{b(u,v)}{\nor{u}_U}$.
\end{itemize}
These three conditions are all related to the inf-sup condition.  The starting point of DPG is to require from the start that $\frac{M}{\gamma} = 1$.  By specifying a test norm, the trial norm  (and consequentially the space $U$) are defined such that we can guarantee that $\frac{M}{\gamma} = 1$ by construction.

\end{enumerate}
\end{enumerate}
\closing{Best regards}

### 2013-05-01 docs/Jesse/HeuerPaper/paper.tex

%&pdflatex
\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

@@

We consider the following model convection-diffusion problem on a domain
$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
\begin{equation}
\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
\end{equation}
which can be cast into the first order form on the group variable
$\LRp{u,\sigma}$ as
\begin{equation}
\eqnlab{CDstrong}
A \LRp{u,\sigma} \coloneqq \LRs {
\begin{array}{c}
\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
\end{array}} = \LRs{
\begin{array}{c}
f \\ 0
\end{array}
}.
\end{equation}
Using the abstract ultra-weak formulation developed in Section
\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
obtain
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
  \jump{v} }_{\Gh},
\end{align*}
where $\LRp{v, \tau}$ is the group test function. It should be pointed
out that the divergence and gradient operators are understood to act
element-wise on test functions $\LRp{v, \tau}$ in the broken graph
space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
canonical test norm can be written as
\[
\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
    div},K)}^2,
\]
where
\[
\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2.
\]

In order to define the proper norm on the trial space, boundary
conditions need to be specified. We begin by splitting the boundary
$\Gamma$ as follows
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
\beta_n(x) = 0\},
\end{align*}
where $\beta_n \coloneqq \beta \cdot n$.
Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
conditions everywhere on $\Gamma$.  
%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
In this paper, we employ the inflow
condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
\]
instead of $\beta_n u = u_0$. The former resembles the latter
as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.

@@

For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm. We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together. Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other. The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments). \textbf{This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions}.

@@

The second step will be to \textbf{show the equivalence of the energy norm to explicit norms on $U$}. Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent. Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$. Specifically, we use the norm on $U$ 
\begin{equation}
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
\end{equation}
For equivalence between norms, two constants are specified. However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$. See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.

@@

We introduce first the bounds derived; the proofs will be given later. For this analysis, it will be necessary to assume certain technical conditions on $\beta$.  For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.  Additionally, we will assume that some or all of the following assumptions hold:
\begin{align}
&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req},\\
&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req},\\
&\div \beta = 0 \label{c_req}.
\end{align}
Under proper assumptions on $\beta$, we have the robust bounds, which are proved in the Appendix. 
\begin{itemize}
\item \textbf{Lemma \ref{lemma_stream}}: \textit{For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
and $v_1 \in H^1(\Omega)$, satisfying equations \eqref{adjoint1} and \eqref{adjoint2} with $f=0$, and with boundary conditions \eqref{bc_1} and \eqref{bc_2}},
\begin{align*}
\|\beta \cdot \grad v_1 \| &\lesssim \| g\|.
\end{align*}
Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
\item \textbf{Lemma \ref{lemma_grad}}: \textit{For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega)$ satisfying equations \eqref{adjoint1} and \eqref{adjoint2} and boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$},
\[
\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \|f\|^2.
\]
We can characterize both $v_1$ and $v_2$ in the above decompositions using this theorem by setting either $f=0$ or $g=0$. 
%\begin{align*}
%\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
%\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
%\end{align*}
%By the triangle inequality, this implies for any $w$ of the form $w=v_1+v_2$
%\begin{align*}
%\epsilon \|\grad w\|^2 + \|w\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
%\end{align*}
\item \textbf{Lemma \ref{lemma_boundary}}: \textit{For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and solutions $v_0 \in H^1(\Oh)$ and $\tau_0 \in H({\rm div},\Oh)$ of equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$,} 
\begin{align*}
\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| \jump{\tau_0\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v_0}\|_{\Gh^0 \cup \Gamma_+}.
\end{align*}
\end{itemize}
We are interested in showing the equivalence of the DPG energy norm with norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively.  We will show this by bounding $\|\cdot \|_V$ from below by $\|\cdot\|_{V,U,1}$ and from above by $\|\cdot\|_{V,U,2}$ (the induced test norms for $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively).

@@

Our test norm, as defined over a single element $K$, is now
\[
\|\left(v,\tau\right)\|_{V,K}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
\]
This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.  This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.

@@

The main theoretical result of this paper can now be given:
\begin{lemma}
Under the mesh-dependent test norm
\[
\|\left(v,\tau\right)\|_{V,\Oh}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
\]
where $C_v, C_{\tau}\in L^2(\Omega)$ are defined elementwise through
\begin{align*}
\left.C_v\right |_K &= \min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}\\
\left.C_{\tau}\right |_K &= \min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}.
\end{align*}
If $\beta$ satisfies \eqref{a_req}, \eqref{b_req}, and \eqref{c_req}, the DPG energy norm $\nor{\cdot}_E$ satisfies the following equivalence relations
\begin{align*}
\nor{u}_{L^2} + \nor{\sigma}_{L^2} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon}\nor{\widehat{f}_n} 
&\lesssim \nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E \\ 
%\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{C_\sigma \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right),
\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{\frac{1}{\epsilon C_\tau} \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right).
\end{align*}
%where $C_\sigma \in L^2(\Omega)$ is defined elementwise through $\left.C_\sigma\right|_K  = \max\left\{ \frac{1}{\sqrt{\epsilon}} , \frac{\sqrt{|K|}}{\epsilon} \right\}$.
\end{lemma}

@@

To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}. For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
\[
\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
\]
which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.  For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
\begin{align*}
u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
\sigma_y &=  0, \quad y=0,1,\\
u &= 0, \quad x=1.\\
\end{align*}
In this case, our exact solution is the series
\[
u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r2) - r_2\exp(-r1)}\cos(n\pi y),
\]
where
\begin{align*}
r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
\lambda_n &= n^2\pi^2 \epsilon.
\end{align*}
The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
\[
C_n = \int_0^1 u_0(y) \cos(n\pi y).
\]

>>>>

\documentclass[11pt,onecolumn]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,amsthm}
\usepackage[top=2cm,bottom=3cm,left=2.5cm,right=2cm]{geometry}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{array}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{algorithm, algorithmic}
\usepackage{array}
\usepackage{bm}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage[normalem]{ulem}
\usepackage{epstopdf}

@@

We consider the following model convection-diffusion problem on a domain
$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
\begin{equation}
\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
\end{equation}
which can be cast into the first order form on the group variable
$\LRp{u,\sigma}$ as
\begin{equation}
\eqnlab{CDstrong}
A \LRp{u,\sigma} \coloneqq \LRs {
\begin{array}{c}
\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
\end{array}} = \LRs{
\begin{array}{c}
f \\ 0
\end{array}
}.
\end{equation}
Using the abstract ultra-weak formulation developed in Section
\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
obtain
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
  \jump{v} }_{\Gh},
\end{align*}
where $\LRp{v, \tau}$ is the group test function. It should be pointed
out that the divergence and gradient operators are understood to act
element-wise on test functions $\LRp{v, \tau}$ in the broken graph
space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
canonical norm on this test space can be written as
\[
\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
    div},K)}^2,
\]
where
\[
\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2.
\]

In order to define the proper norm on the trial space, boundary
conditions need to be specified. We begin by splitting the boundary
$\Gamma$ as follows
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
\beta_n(x) = 0\},
\end{align*}
where $\beta_n \coloneqq \beta \cdot n$.
Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
conditions everywhere on $\Gamma$.  
%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
In this paper, we employ the inflow
condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
\]
instead of $\beta_n u = u_0$. The former resembles the latter as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG. Physically speaking, as the above boundary condition corresponds to the integration by parts of the conservation equation, a boundary condition on $\beta_n u - \sigma_n$ models a boundary condition on the conserved flux.

@@

For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm. We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together. Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other. The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments). This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions.

@@

The second step will be to show the equivalence of the energy norm to explicit norms on $U$. Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent. Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$. Specifically, we use the norm on $U$ 
\begin{equation}
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
\end{equation}
For equivalence between norms, two constants are specified. However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$. See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.

@@

We introduce first the bounds derived; the proofs will be given later. For this analysis, it will be necessary to assume certain technical conditions on $\beta$.  For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.  Additionally, we will assume that some or all of the following assumptions hold
\footnote{These assumptions correspond to convection fields which are divergence-free \eqref{c_req}, curl-free \eqref{a_req}, bounded away from zero \eqref{a_req}, and of bounded variation \eqref{b_req}.  However, these are merely sufficient conditions; numerical experiments indicate that they may not be strictly necessary.}
:
\begin{align}
&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req},\\
&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req},\\
&\div \beta = 0 \label{c_req}.
\end{align}

Under these assumptions on $\beta$, we have the following robust bounds, which are proved in the Appendix. 
\begin{itemize}
\item \textbf{Lemma \ref{lemma_stream}}: \textit{For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, %$f=0$ 
and $v_1 \in H^1(\Omega)$, satisfying equations \eqref{adjoint1} and \eqref{adjoint2} with $f=0$, and with boundary conditions \eqref{bc_1} and \eqref{bc_2}},
\begin{align*}
\|\beta \cdot \grad v_1 \| &\lesssim \| g\|.
\end{align*}
Similarly, from $\div \tau_1 - \beta\cdot \grad v_1 = g$, we get $\|\div \tau_1\| \lesssim \|g\|$ as well.  
\item \textbf{Lemma \ref{lemma_grad}}: \textit{For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega)$ satisfying equations \eqref{adjoint1} and \eqref{adjoint2} and boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$},
\[
\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim \|g\|^2 + \epsilon \|f\|^2.
\]
We can characterize both $v_1$ and $v_2$ in the above decompositions using this theorem by setting either $f=0$ or $g=0$. 
%\begin{align*}
%\epsilon \|\grad v_1\|^2 + \|v_1\|^2 &\lesssim \|g\|^2\\
%\epsilon \|\grad v_2\|^2 + \|v_2\|^2 &\lesssim \epsilon \| f\|^2.
%\end{align*}
%By the triangle inequality, this implies for any $w$ of the form $w=v_1+v_2$
%\begin{align*}
%\epsilon \|\grad w\|^2 + \|w\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
%\end{align*}
\item \textbf{Lemma \ref{lemma_boundary}}: \textit{For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and solutions $v_0 \in H^1(\Oh)$ and $\tau_0 \in H({\rm div},\Oh)$ of equations \eqref{adjoint1} and \eqref{adjoint2} with $f=g=0$,} 
\begin{align*}
\|\grad v_0\| = \frac{1}{\epsilon}\|\tau_0\| &\lesssim \frac{1}{\epsilon} \| \jump{\tau_0\cdot n}\|_{\Gh \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| \jump{v_0}\|_{\Gh^0 \cup \Gamma_+}.
\end{align*}
\end{itemize}
We are interested in showing the equivalence of the DPG energy norm with norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively.  We will show this by bounding $\|\cdot \|_V$ from below by $\|\cdot\|_{V,U,1}$ and from above by $\|\cdot\|_{V,U,2}$ (the induced test norms for $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$, respectively).

@@

We can now define $\nor{\LRp{v,\tau}}_{V(K)}$, our test norm over a single element $K$, as 
\[
\|\left(v,\tau\right)\|_{V(K)}^2 = \min\left\{\frac{\epsilon}{|K|},1\right\}\|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \min\left\{\frac{1}{\epsilon},\frac{1}{|K|}\right\}\|\tau\|^2.
\]
This modified test norm avoids boundary layers in the locally computed optimal test functions, but for adaptive meshes, provides additional stability in areas of heavy refinement, where the best approximation error tends to be large and stronger robustness is most necessary.  This leads to a test norm which produces easily approximable optimal test functions, but still provides \textit{asymptotically} the strongest test norm and tightest robustness results in the areas of highest error.

@@

The main theoretical result of this paper can now be given:
\begin{lemma}
Under the mesh-dependent test norm
\[
\|\left(v,\tau\right)\|_{V(\Oh)}^2 = \|C_vv\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \|C_\tau\tau\|^2,
\]
where $C_v, C_{\tau}\in L^2(\Omega)$ are defined elementwise through
\begin{align*}
\left.C_v\right |_K &= \min\left\{\sqrt{\frac{\epsilon}{|K|}},1\right\}\\
\left.C_{\tau}\right |_K &= \min\left\{\frac{1}{\sqrt{\epsilon}},\frac{1}{\sqrt{|K|}}\right\}.
\end{align*}
If $\beta$ satisfies \eqref{a_req}, \eqref{b_req}, and \eqref{c_req}, the DPG energy norm $\nor{\cdot}_E$ satisfies the following equivalence relations
\begin{align*}
\nor{u}_{L^2} + \nor{\sigma}_{L^2} + \epsilon\nor{\widehat{u}} + \sqrt{\epsilon}\nor{\widehat{f}_n} 
&\lesssim \nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E \\ 
%\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{C_\sigma \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right),
\nor{\left(u,\sigma, \widehat{u},\widehat{f}_n\right)}_E &\lesssim \nor{u}_{L^2} + \nor{\frac{1}{\epsilon C_\tau} \sigma}_{L^2} + \frac{1}{\sqrt{\epsilon}} \left(\nor{\widehat{u}} + \nor{\widehat{f}_n}\right).
\end{align*}
%where $C_\sigma \in L^2(\Omega)$ is defined elementwise through $\left.C_\sigma\right|_K  = \max\left\{ \frac{1}{\sqrt{\epsilon}} , \frac{\sqrt{|K|}}{\epsilon} \right\}$.
\end{lemma}

@@

To confirm our theoretical results, we adopt a modification of a problem first proposed by Eriksson and Johnson in \cite{Eriksson1993}. For the choice of $\Omega = (0,1)^2$, $f=0$, and $\beta = (1,0)^T$, the convection diffusion equation reduces to
\[
\pd{u}{x} - \epsilon \left(\pdd{u}{x}+ \pdd{u}{y}\right) = 0,
\]
which has an exact solution by separation of variables, allowing us to analyze convergence of DPG for a wide range of $\epsilon$.  For boundary conditions, we impose $u=0$ on $\Gamma_+$ and $\beta_n u - \sigma_n$ on $\Gamma_-$, which reduces to
\begin{align*}
u-\sigma_x &= u_0-\sigma_{x,0}, \quad x=0,\\
\sigma_y &=  0, \quad y=0,1,\\
u &= 0, \quad x=1.\\
\end{align*}
In this case, our exact solution is the series
\[
u(x,y) = C_0 + \sum_{n=1}^\infty C_n \frac{\exp(r_2(x-1)-\exp(r_1(x-1)))}{r_1\exp(-r_2) - r_2\exp(-r_1)}\cos(n\pi y),
\]
where
\begin{align*}
r_{1,2} &= \frac{1 \pm \sqrt{1 + 4 \epsilon\lambda_n}}{2 \epsilon},\\
\lambda_n &= n^2\pi^2 \epsilon.
\end{align*}
The constants $C_n$ depend on a given inflow condition $u_0$ at $x=0$ via the formula
\[
C_n = \int_0^1 u_0(y) \cos(n\pi y).
\]
